---
title: "Computer Assignment 1a - Econometrics I"
author: "Jane Birkin, Serge Gainsbourg, Brigitte Bardot"
date: "August 30, 2022"
output:
  pdf_document: default
  word_document: default
---

```{r clear memory, include=FALSE}
# Clear plots
if(!is.null(dev.list())) dev.off()
# Clear console
cat("\014") 
# Clean workspace
rm(list=ls())

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = "hide")
```

# I. Preliminaries

**Clearing workspace**

To remove all the objects that are stored in your global environment (but not remove any loaded packages):
```{r clear memory, results="hide"}
# Clear plots
if(!is.null(dev.list())) dev.off()
# Clear console
cat("\014") 
# Clean workspace
rm(list=ls())
```

**Packages**

To put all packages (that were previously installed) into memory:

```{r, warning=FALSE, message=FALSE}
library(foreign)
library(tidyverse)
library(dagitty)
library(ggdag)
library(dplyr)
library(tinytex)
library(stargazer)
library(readstata13)
```


# II. Introduction to the assignment

To load the dataset into memory:

```{r load data}
theUrl <- "https://surfdrive.surf.nl/files/index.php/s/j9uSZ4dPSkyqInX/download"
burglary <- read.dta13 (file = theUrl)
```

# IV. Causal diagram: visualizing selection into treatment

To define the causal diagram:

```{r nodes}
ca1a <- dagitty('dag{
                dog [pos="0,0"]
                burgl [pos="2,0"]
                athome [pos="1,2"]
                
                dog <- athome -> burgl
                dog -> burgl
                }')

```

Plot the causal diagram with *ggdag* as follows:

```{r diagram plot, out.width = "60%"}
ggdag(ca1a)
```
# V. Descriptive statistics

To report the mean (weighted) rate of victimization for households with and without a dog:

```{r descriptive statistics}
sumburglary <- burglary %>%
            group_by(dog) %>%
            summarise(mean_burgl = weighted.mean(burglary,hhweight))
sumburglary
```

If we want to produce similar summary statistics for a subgroup, say homeowners, we can use the function *filter* as follows:

```{r descriptive statistics 2}
sumburglary <- burglary %>%
            filter(homeowner==1) %>%
            group_by(dog) %>%
            summarise(mean_burgl = weighted.mean(burglary,hhweight))
sumburglary
```

Etcetera (the above should provide a good start for making your first assignment for Econometrics 1)

```{r}
sumathome <- burglary %>%
group_by(dog) %>%
summarise(mean_athome = weighted.mean(notathome20,hhweight))

sumathome
```

```{r}
summary(lm(burglary ~ dog, data=burglary))

```


```{r}
naive <- lm(burglary ~ dog, data=burglary)
stargazer(naive)

```
```{r}
summary(lm(burglary ~ dog + notathome20, data=burglary))

```

